Modeling site-specific amino-acid preferences deepens phylogenetic estimates of the divergence of viral proteins.

### 2018-03-08 manuscript/manuscript.tex
added reference to stoke shift paper

The fact that an ExpCM has the greatest effect on branches close to the sequence used in the experiment can be rationalized in terms of existing knowledge about how epistasis shifts protein amino-acid preferences during evolution~\jdbcomment{Stokes shift paper, Shah et al paper, Doud et al 2015, Haddox et al 2018, look at other papers cited about Stokes shift in Haddox et al 2018}.
In reality, sites in proteins do not have completely conserved site-specific amino-acid preferences. 
Rather, the effect of a mutation at one site in a protein can depend on the amino-acid identity of other sites in the protein~\jdbcomment{Maybe cite a couple of general papers on epistasis, some good ones in Haddox et al 2018}. 
The deep mutational scanning experiments that inform our ExpCM's were performed in the context of a single HA genetic background, and so do not account for how such epistatic interactions can cause amino-acid preferences to shift as substitutions accumulate. 
Therefore, it makes sense that an ExpCM would most accurately describe the evolution of sequences closely related to the one used in the experiment.

>>>>

The fact that an ExpCM has the greatest effect on branches close to the sequence used in the experiment can be rationalized in terms of existing knowledge about how epistasis shifts protein amino-acid preferences during evolution~\citep{pollock2012amino, shah2015contingency, doud2015site, haddox2017mapping, risso2014mutational}.
In reality, sites in proteins do not have completely conserved site-specific amino-acid preferences. 
Rather, the effect of a mutation at one site in a protein can depend on the amino-acid identity of other sites in the protein~\citep{starr2018pervasive, pollock2012amino, shah2015contingency, bazykin2015changing}. 
The deep mutational scanning experiments that inform our ExpCM's were performed in the context of a single HA genetic background, and so do not account for how such epistatic interactions can cause amino-acid preferences to shift as substitutions accumulate. 
Therefore, it makes sense that an ExpCM would most accurately describe the evolution of sequences closely related to the one used in the experiment.
